Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-06 documentation/paper.tex
Added data for ICN accuracy as a function of hyperparameters

@@

As seen in Figure \ref{icn_grid_search}, the network learned to replicate Acoustic Parameter very accurately. Interestingly, the examples with Acoustic Parameter values between the neutron and alpha particle ranges were also classified as such by the network.

>>>>

As seen in Figure \ref{icn_grid_search}, the network learned to replicate Acoustic Parameter very accurately. Interestingly, the examples with Acoustic Parameter values between the neutron and alpha particle ranges were also classified as such by the network. This may imply the indecisiveness on these examples is fundamental to the data rather than an implementation problem with Acoustic Parameter.

@@

Digging deeper into the performance throughout the runs of the grid search, Figure \ref{icn_acc_by_hyper} shows the mean accuracy as a function of each of the hyperparameters that were optimized. Dropout has a clear effect, with 25\% shown to be the optimal number of neurons to drop. L2 regularization is also significant; all $\lambda$ values greater than 0 make performance worse.

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{icn_acc_by_hyper}
    \caption{\label{icn_acc_by_hyper} Mean accuracy of iterative cluster nucleation as a function of hyperparameter values.}
\end{figure}
